---
title: "Homework 3"
author: "Rachel Bittner"
format: html
editor: visual
---

GitHub Repository: https://github.com/bittnation/ENVS-193DS_homework-03.git

```{r reading-packages}

library(tidyverse)
library(here)
library(flextable)
library(janitor)

```

# Problem 1. Personal Data

## a. Data Summarizing

I could calculate the mean hours of productivity to compare between locations, such as home versus the library, because I suspect that my environment affects how focused I am. This comparison would help determine if studying in the library leads to longer or more productive work sessions than working at home.

## b. Visualization

```{r}
list.files()
```


```{r cleaning-data}

presonal_data <- read_csv("ENVS 193 DS - Personal Data - sheet1.numbers")
  
  
  
  
  
personal_data_clean <-  |> # use the production data frame
  clean_names() |> # clean up column names
  filter(entity == "United States") |> # filter to only include observations from the US
  select(year, aquaculture_production_metric_tons, capture_fisheries_production_metric_tons) |> # select columns of interest 
  pivot_longer(cols = aquaculture_production_metric_tons:capture_fisheries_production_metric_tons, # choose columns to pivot
               names_to = "type", # name the column name with fishery type "type"
               values_to = "catch_metric_tons") |> # name the column name with the catch amount "catch_metric_tons"
  mutate(type = case_when( # mutate the existing type column
    type == "aquaculture_production_metric_tons" ~ "aquaculture", # when "aquaculture_production_metric_tons" appears in the "type" column, fill in "aquaculture"
    type == "capture_fisheries_production_metric_tons" ~ "capture" # when "capture_fisheries_production_metric_tons" appears in the "type" column, fill in "capture"
  )) |> 
  mutate(metric_tons_mil = catch_metric_tons/1000000) # convert catch in metric tons to millions




```


```{r data-plot}
# base layer: ggplot
ggplot(data = production_clean,
       aes(x = type, 
           y = metric_tons_mil, 
           color = type)) +
  # first layer: adding data (each point shows an observation)
  geom_jitter(width = 0.1,
              height = 0,
              alpha = 0.4,
              shape = 21) +
  # second layer: means and 95% CI
  geom_pointrange(data = production_summary,
                  aes(x = type, 
                      y = mean, 
                      ymin = mean - margin, 
                      ymax = mean + margin)) +
  # changing appearance: colors, labels, and theme
  scale_color_manual(values = c("aquaculture" = "deeppink3",
                                "capture" = "slateblue4")) +
  labs(x = "Production type",
       y = "Million metric tons of production",
       color = "Production type",
       title = "Capture produces more than aquaculture") +
  theme_light()
```

\[insert written response here\]

## c. Caption

```{r}
# insert code here
```

\[insert written response here\]

## d. Table Presentation

```{r}
# insert code here
```

\[insert written response here\]

# Problem 2. Affective Visualization

## a. describe affective visualization

```{r}
# insert code here
```

## b. sketch

```{r}
# insert code here
```

## c. visualization draft

\[insert written response here\]

## d. artist statement


# Problem 3. Statistical Critique 

```{r}
# insert any cleaning/wrangling code you need here
```

## a. Revist and summerarize

```{r}
# insert code here
```

## b. Visual clarity

```{r}
# insert code here
```

## c. Aesthetic calrity

\[insert written response here\]

## d. Recommendations

