---
title: "Homework 3"
author: "Rachel Bittner"
format: html
editor: visual
---

GitHub Repository: https://github.com/bittnation/ENVS-193DS_homework-03.git

```{r reading-packages}

library(tidyverse)
library(here)
library(flextable)
library(janitor)

```

# Problem 1. Personal Data

## a. Data Summarizing

I could calculate the mean hours of productivity to compare between locations, such as home versus the library, because I suspect that my environment affects how focused I am. This comparison would help determine if studying in the library leads to longer or more productive work sessions than working at home.

## b. Visualization


```{r}

personal_data <- read_csv("Personal_data_1.csv") #reading in data frame

```

```{r  cleaning-data}  

personal_data_clean <- personal_data |>
   clean_names() |>
   filter(location %in% c("Home", "Library")) |> #filter to include only observations from home and library
  select(hours_of_productivity_hh_mm, location) |> #selecting only the columns with data of interest
  separate(hours_of_productivity_hh_mm, into = c("hrs", "mins"), sep = ":", convert = TRUE) |>
  mutate(productivity_hours = hrs + mins / 60) #separating hours and minutes to calculate productivity in terms of hours

```



```{r data-plot}
ggplot(data = personal_data_clean, #choosing data set
       aes(x = location, 
           y = productivity_hours, 
           fill = location)) + #setting axis 
  geom_boxplot() +
  geom_jitter(height = 0, width = 0.2, alpha = 0.6) +
  scale_fill_manual(values = c("Home" = "#008080", "Library" = "#800080")) + #choosing custom colors 
  theme_minimal() +
  labs(title = "Distribution of Productivity Hours by Location", #giving plot a title
       x = "Location", y = "Productivity (hours)") + #labeling axis
  theme(legend.position = "none")  #removing legend


```


## c. Caption

Figure 1. Boxplot with jittered points showing the distribution of daily productivity hours at home and in the library. Time values were converted from HH:MM to decimal format to compare average productivity between locations. The figure highlights noticeable differences in productivity patterns depending on where studying takes place


## d. Table Presentation

```{r}
# insert code here
```

\[insert written response here\]

# Problem 2. Affective Visualization

## a. describe affective visualization

```{r}
# insert code here
```

## b. sketch

```{r}
# insert code here
```

## c. visualization draft

\[insert written response here\]

## d. artist statement


# Problem 3. Statistical Critique 

```{r}
# insert any cleaning/wrangling code you need here
```

## a. Revist and summerarize

```{r}
# insert code here
```

## b. Visual clarity

```{r}
# insert code here
```

## c. Aesthetic calrity

\[insert written response here\]

## d. Recommendations

