---
title: "Homework 3"
author: "Rachel Bittner"
format: html
editor: visual
---

GitHub Repository: https://github.com/bittnation/ENVS-193DS_homework-03.git

```{r reading-packages}

library(tidyverse)
library(here)
library(flextable)
library(janitor)

```

# Problem 1. Personal Data

## a. Data Summarizing

I could calculate the mean hours of productivity to compare between locations, such as home versus the library, because I suspect that my environment affects how focused I am. This comparison would help determine if studying in the library leads to longer or more productive work sessions than working at home.

## b. Visualization

```{r}
# insert code here
```

\[insert written response here\]

## c. Caption

```{r}
# insert code here
```

\[insert written response here\]

## d. Table Presentation

```{r}
# insert code here
```

\[insert written response here\]

# Problem 2. Affective Visualization

## a. describe affective visualization

```{r}
# insert code here
```

## b. sketch

```{r}
# insert code here
```

## c. visualization draft

\[insert written response here\]

## d. artist statement


# Problem 3. Statistical Critique 

```{r}
# insert any cleaning/wrangling code you need here
```

## a. Revist and summerarize

```{r}
# insert code here
```

## b. Visual clarity

```{r}
# insert code here
```

## c. Aesthetic calrity

\[insert written response here\]

## d. Recommendations

