---
title: "Homework 3"
author: "Rachel Bittner"
format: html
editor: visual
---

GitHub Repository: https://github.com/bittnation/ENVS-193DS_homework-03.git

```{r reading-packages}

library(tidyverse)
library(here)
library(flextable)
library(janitor)
library(dplyr)

```

# Problem 1. Personal Data

## a. Data Summarizing

I could calculate the mean hours of productivity to compare between locations, such as home versus the library, because I suspect that my environment affects how focused I am. This comparison would help determine if studying in the library leads to longer or more productive work sessions than working at home.

## b. Visualization

```{r}

personal_data <- read_csv("Personal_data_1.csv") #reading in data frame

```

```{r  cleaning-data}

personal_data_clean <- personal_data |>
   clean_names() |>
   filter(location %in% c("Home", "Library")) |> #filter to include only observations from home and library
  select(hours_of_productivity_hh_mm, location) |> #selecting only the columns with data of interest
  separate(hours_of_productivity_hh_mm, into = c("hrs", "mins"), sep = ":", convert = TRUE) |>
  mutate(productivity_hours = hrs + mins / 60) #separating hours and minutes to calculate productivity in terms of hours

```

```{r data-plot}
ggplot(data = personal_data_clean, #choosing data set
       aes(x = location, 
           y = productivity_hours, 
           fill = location)) + #setting axis 
  geom_boxplot() +
  geom_jitter(height = 0, width = 0.2, alpha = 0.6) +
  scale_fill_manual(values = c("Home" = "#008080", "Library" = "#800080")) + #choosing custom colors 
  theme_minimal() +
  labs(title = "Distribution of Productivity Hours by Location", #giving plot a title
       x = "Location", y = "Productivity (hours)") + #labeling axis
  theme(legend.position = "none")  #removing legend


```

**Figure 1.** Boxplot showing the distribution of daily productivity hours by location. Each box represents the interquartile range (IQR) of productivity values, with the horizontal line indicating the median. Whiskers extend to values within 1.5 times the IQR, and individual points represent daily observations. Fill colors indicate study location: teal for Home (n = 7) and purple for Library (n = 8). Productivity hours were calculated by converting reported time values from HH:MM format to decimal hours.

## d. Table Presentation

```{r table}

summary_table <- personal_data_clean |> #creating summary data set
  group_by(location) |> #grouping all values by location: Library or home
  summarise(
    n = n(), #including sample size
    mean_productivity = round(mean(productivity_hours, na.rm = TRUE), 1),#calculating mean hours of productivity and rounding to one decimal point
    sd_productivity = round(sd(productivity_hours, na.rm = TRUE), 1) # calculating standard deviation in hours and rounding to one decimal point
  )

summary_table |> #putting calculated values into the format of a summary table
  flextable() |>
  set_header_labels( #labeling column headers
    location = "Location",
    n = "Sample Size (n)",
    mean_productivity = "Mean Productivity (hours)",
    sd_productivity = "SD (hours)"
  ) |>
  autofit() |> # cleaning table format
  set_caption("Table 1. Summary of productivity hours by location.") #captioning summary table
```

Table 1. Summary of productivity hours by location

# Problem 2. Affective Visualization

## a.

An affective visualization of my personal data could be a calendar drawing where each day includes a small symbolic drawing to represent the location (a house icon for Home and a stack of books for the Library). The background color of each day would reflect how productive I was, with bold or bright colors for days higher productivity and opaque colors for low productivity (brightness ranging from highest productivity being the brightest and lowest productivity being the dullest). Lines layered over the color would represent caffeine intake, with sharp or thick lines showing higher caffeine intake and faint, smooth lines showing less (no lines for no caffeine). This visualization wouldn’t focus on exact data values but would instead capture the feel of each day through visual elements that reflect data regarding mood, energy, and environment.

## b. 

![](images/problem-2-part-b.pdf)

## c. visualization draft

\[insert written response here\]

## d. artist statement

# Problem 3. Statistical Critique

```{r}
# insert any cleaning/wrangling code you need here
```

## a. Revist and summerarize

```{r}
# insert code here
```

## b. Visual clarity

```{r}
# insert code here
```

## c. Aesthetic calrity

\[insert written response here\]

## d. Recommendations
